\pkg{cubble}: An R Package for Structuring Spatio-temporal Data

### 2022-02-21 main.Rmd
more work on abstract

---
documentclass: jss
author:
  - name: H. Sherry Zhang
    affiliation: Monash University
    address: 21 Chancellors Walk, Clayton VIC 3800 Australia
    email: \email{huize.zhang@monash.edu}
  - name: Dianne Cook
    affiliation: 'Monash University \AND'
    address: 21 Chancellors Walk, Clayton VIC 3800 Australia
    # location: Melbourne, Australia
    email:  dicook@monash.edu
  - name: Ursula Laa
    affiliation: 'University of Natural Resources and Life Sciences \AND'
    address: Gregor-Mendel-Straße 33, 1180 Wien, Austria
    email:  ursula.laa@boku.ac.at
  - name: Nicolas Langrené
    affiliation: 'BNU-HKBU United International College \AND'
    address: 2000 Jintong Road, Tangjiawan, Zhuhai, Guangdong Province, China
    email: nicolas@langrene.com
  - name: Patricia Menéndez
    affiliation: 'Monash University \AND'
    address: 21 Chancellors Walk, Clayton VIC 3800 Australia
    email:  patricia.menendez@monash.edu
title:
  formatted: "\\pkg{cubble}: An R Package for Structuring Spatio-temporal Data"
  # If you use tex in the formatted title, alsoge supply version without
  plain:     "cubble: An R Package for Structuring Spatio-temporal Data"
  # For running headers, if needed
  # short:     "\\pkg{foo}: A Capitalized Title"
abstract: >
  Spatio-temporal variables can be time invariant or not and this divides them into those can be identified only with the spatial identifier and those cross-identified by the spatial and temporal identifier. In this paper, a new data structure, \code{cubble}, is proposed for manipulating and visualising spatio-temporal data. The new data structure proposes two forms for manipulating the spatial and temporal dimension separately while providing a smooth switch between the two forms to link the two dimensions. Advanced considerations are given to illustrate data with hierarchical structure, data matching, and how \pkg{cubble} fits with interactive graphics pipeline. Examples are given to analysing Australia meteorology data, river level data, and climate reanalysis (ERA5). 
keywords:
  # at least one keyword must be supplied
  formatted: [spatio temporal,  "\\proglang{R}", climate weather station, data analysis]
  plain:     [spatio temporal, R, climate weather station, data analysis]
preamble: >
  \usepackage{amsmath}
  \usepackage{array}
  \usepackage{xcolor}
output: rticles::jss_article
bibliography: references.bib
---

>>>>

---
documentclass: jss
author:
  - name: H. Sherry Zhang
    affiliation: Monash University
    address: 21 Chancellors Walk, Clayton VIC 3800 Australia
    email: \email{huize.zhang@monash.edu}
  - name: Dianne Cook
    affiliation: 'Monash University \AND'
    address: 21 Chancellors Walk, Clayton VIC 3800 Australia
    # location: Melbourne, Australia
    email:  dicook@monash.edu
  - name: Ursula Laa
    affiliation: 'University of Natural Resources and Life Sciences \AND'
    address: Gregor-Mendel-Straße 33, 1180 Wien, Austria
    email:  ursula.laa@boku.ac.at
  - name: Nicolas Langrené
    affiliation: 'BNU-HKBU United International College \AND'
    address: 2000 Jintong Road, Tangjiawan, Zhuhai, Guangdong Province, China
    email: nicolas@langrene.com
  - name: Patricia Menéndez
    affiliation: 'Monash University \AND'
    address: 21 Chancellors Walk, Clayton VIC 3800 Australia
    email:  patricia.menendez@monash.edu
title:
  formatted: "\\pkg{cubble}: An R Package for Structuring Spatio-temporal Data"
  # If you use tex in the formatted title, alsoge supply version without
  plain:     "cubble: An R Package for Structuring Spatio-temporal Data"
  # For running headers, if needed
  # short:     "\\pkg{foo}: A Capitalized Title"
abstract: >
  Exploring spatio-temporal data can sometimes be discouraging given the various different formats spatio-temporal data can present themselves in practice. Moreover, the two observational units naturally exist in spatio-temporal data can cost analysts many time and efforts on organising variables and results and switching between a single table and multiple tables in the analysis. In this paper, a new data structure, \code{cubble}, is proposed for wrangling and visualising spatio-temporal data. The new data structure uses a single data object to organise spatial and temporal variables in two forms so that they can be wrangled separately while keep syncronised. Advanced considerations are given to illustrate data with hierarchical structure, data matching, how cubble fits with the interactive graphics pipeline, and spatio-temporal transformation. Examples are given to analysing Australia meteorology data, river level data, and climate reanalysis (ERA5). 
keywords:
  # at least one keyword must be supplied
  formatted: [spatio temporal,  "\\proglang{R}", climate weather station, data analysis]
  plain:     [spatio temporal, R, climate weather station, data analysis]
preamble: >
  \usepackage{amsmath}
  \usepackage{array}
  \usepackage{xcolor}
output: rticles::jss_article
bibliography: references.bib
---

### 2022-02-21 main.tex
more work on abstract

\Abstract{
Spatio-temporal variables can be divided into time invariant ones that
can be identified by the spatial identifier, or the time varying ones
that cross-identified by the spatial and temporal identifiers. In this
paper, a new data structure, \code{cubble}, is proposed for manipulating
and visualising spatio-temporal data. The new data structure uses two
forms to organise time invariant and varying variables so that the
spatial and temporal dimension of the data can be manipulated separately
while keep synchronised. Advanced considerations are given to illustrate
data with hierarchical structure, data matching, and how cubble fits
with the interactive graphics pipeline. Examples are given to analysing
Australia meteorology data, river level data, and climate reanalysis
(ERA5).
}

>>>>

\Abstract{
Exploring spatio-temporal data can sometimes be discouraging given the
various different formats spatio-temporal data can present themselves in
practice. Moreover, the two observational units naturally exist in
spatio-temporal data can cost analysts many time and efforts on
organising variables and results and switching between a single table
and multiple tables in the analysis. In this paper, a new data
structure, \code{cubble}, is proposed for wrangling and visualising
spatio-temporal data. The new data structure uses a single data object
to organise spatial and temporal variables in two forms so that they can
be wrangled separately while keep syncronised. Advanced considerations
are given to illustrate data with hierarchical structure, data matching,
how cubble fits with the interactive graphics pipeline, and
spatio-temporal transformation. Examples are given to analysing
Australia meteorology data, river level data, and climate reanalysis
(ERA5).
}
